ShabbyPages: A Recipe for Repeatable, Synthetic, Modern Document Images

### 2023-01-23 paper/paper.tex
add diversity metric

\begin{table}
\centering
\caption{Document Image Dataset Feature Comparison}\label{tab1}
\begin{tabular}{|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|}
\hline
Feature & ShabbyPages & NoisyOffice & RVL-CDIP & Tobacco800 \\
\hline
Images & 6202 & 72 & 400000 & 1290\\
Document-specific & Yes & Yes & Yes & Yes\\
Synthetic & Yes & Yes & No & No\\
Groundtruthed? & Yes & Yes & No & No\\
Font size & Multiple & 16pt & Multiple & Multiple\\
Paper styles & Multiple & 1 & Multiple & Multiple\\
Multilingual & Yes & No & No & No\\
Documents contain images? & Yes & No & Yes & Yes\\
Pre-categorized & No & No & Yes & Yes\\
\hline
\end{tabular}
\end{table}

>>>>

\textbf{Diversity.} We use the diversity metric as defined in \cite{kang-etal-2018-data,larson-etal-2019-outlier} to help us measure how diverse a dataset is.
This metric is defined as 
$$
Diversity(X) = \frac{1}{|X|^2} \sum_{a\in X} \sum_{b\in X} \|f(a)-f(b)\|_2
$$
where $f(\cdot)$ is an embedding function mapping the input image into an \emph{n}-dimensional vector space.
Here, we use CLIP's ViT model \cite{clip}, which embeds each image into a 512-dimensional embedding space.
The intuition behind the diversity metric is that datasets where images are highly similar will have lower diversity scores, and datasets where images share less visual similarity will have higher diversity scores.
A dataset with low diversity might not be representative enough of the real world, and low diversity may often correlate with task easiness.

\begin{table}
\centering
\caption{Document Image Dataset Feature Comparison}\label{tab1}
\begin{tabular}{|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|@{\hspace{1em}}l@{\qquad}|}
\hline
Feature & ShabbyPages & NoisyOffice & RVL-CDIP & Tobacco800 \\
\hline
Images & 6202 & 72 & 400000 & 1290\\
Diversity & 0.488 & 0.317 & & \\
Document-specific & Yes & Yes & Yes & Yes\\
Synthetic & Yes & Yes & No & No\\
Groundtruthed? & Yes & Yes & No & No\\
Font size & Multiple & 16pt & Multiple & Multiple\\
Paper styles & Multiple & 1 & Multiple & Multiple\\
Multilingual & Yes & No & No & No\\
Documents contain images? & Yes & No & Yes & Yes\\
Pre-categorized & No & No & Yes & Yes\\
\hline
\end{tabular}
\end{table}
